Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-03-12 papers/eccv2018/4_results.tex
trying different feature generation

>>>>

\subsubsection{System} All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. All code is written in Python and will be freely available upon paper decision. We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.
